A Dependently Typed Multi-Stage Calculus \ifnotanonymous\thanks{Supported by organization x.}\fi

### 2019-06-11 main.tex
Revise substituition of stage variable.

% 自由変数
As usual, the variable $x$ is bound in $\lambda x:\tau.M$
and the transition variable $\alpha$ is bound in $\Lambda \alpha.M$.
We identify $\alpha$-convertible terms and assume the names of bound variables are pairwise distinct.

% Contexts
Contexts are sequences of triples of a variable, its type, and its stage.
We write $\FV(M)$ and $\FTV(M)$ for the set of free variables and the set of free stage variables in $M$, respectively.
$\textrm{Domain}$ is a function from a content to a set of variables defined in the context.
The side condition of $x\not\in\textrm{Domain}(\G)$ prevent multiple appearances of the same variable and
$x\not\in\textrm{FV}(\tau)$ is needed in the proof of Substitution Lemmas.

@@

\begin{align*}
	% \newcommand{\SB}{}
	(\lambda x:\tau.M)[\alpha \mapsto \epsilon] & = \lambda x:\tau[\alpha \mapsto \epsilon].M[\alpha \mapsto \epsilon]                                  \\
	(M\ N)[\alpha \mapsto \epsilon]             & = (M[\alpha \mapsto \epsilon])\ (N[\alpha \mapsto \epsilon])                                          \\
	(\TB_\beta M)[\alpha \mapsto \epsilon]      & = \TB_{\beta[\alpha \mapsto \epsilon]} M[\alpha \mapsto \epsilon]                                     \\
	(\TBL_\beta M)[\alpha \mapsto \epsilon]     & = \TBL_{\beta[\alpha \mapsto \epsilon]} M[\alpha \mapsto \epsilon]                                    \\
	(\Lambda\beta.M)[\alpha \mapsto \epsilon]   & = \Lambda\beta.M[\alpha \mapsto \epsilon]                            & (\text{if } \alpha \neq \beta) \\
	(\Lambda\beta.M)[\alpha \mapsto \epsilon]   & = \Lambda\beta.M                                                     & (\text{if } \alpha = \beta)    \\
	(M\ \epsilon)[\alpha \mapsto \epsilon]      & = M[\alpha \mapsto \epsilon]\ \epsilon                                                                \\
	(\%_\beta M)[\alpha \mapsto \epsilon]       & = \%_{\beta[\alpha \mapsto \epsilon]}M[\alpha \mapsto \epsilon] 
\end{align*}

@@

% \section{First Section}
% \subsection{A Subsection Sample}
% Please note that the first paragraph of a section or subsection is
% not indented. The first paragraph that follows a table, figure,
% equation etc. does not need an indent, either.
% 
% Subsequent paragraphs, however, are indented.
% 
% \subsubsection{Sample Heading (Third Level)} Only two levels of
% headings should be numbered. Lower level headings remain unnumbered;
% they are formatted as run-in headings.
% 
% \paragraph{Sample Heading (Fourth Level)}
% The contribution should contain no more than four levels of
% headings. Table~\ref{tab1} gives a summary of all heading levels.
% 
% \begin{table}
% \caption{Table captions should be placed above the
% tables.}\label{tab1}
% \begin{tabular}{|l|l|l|}
% \hline
% Heading level &  Example & Font size and style\\
% \hline
% Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
% 1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
% 2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
% 3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
% 4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
% \hline
% \end{tabular}
% \end{table}
% 
% 
% \noindent Displayed equations are centered and set on a separate
% line.
% \begin{equation}
% x + y = z
% \end{equation}
% Please try to avoid rasterized images for line-art diagrams and
% schemas. Whenever possible, use vector graphics instead (see
% Fig.~\ref{fig1}).
% 
% \begin{figure}
% \includegraphics[width=\textwidth]{fig1.eps}
% \caption{A figure caption is always placed below the illustration.
% Please note that short captions are centered, while long ones are
% justified by the macro package automatically.} \label{fig1}
% \end{figure}
% 
% \begin{theorem}
% This is a sample theorem. The run-in heading is set in bold, while
% the following text appears in italics. Definitions, lemmas,
% propositions, and corollaries are styled the same way.
% \end{theorem}
% %
% % the environments 'definition', 'lemma', 'proposition', 'corollary',
% % 'remark', and 'example' are defined in the LLNCS documentclass as well.
% %
% \begin{proof}
% Proofs, examples, and remarks have the initial word in italics,
% while the following text appears in normal font.
% \end{proof}
% For citations of references, we prefer the use of square brackets
% and consecutive numbers. Citations using labels or the author/year
% convention are also acceptable. The following bibliography provides
% a sample reference list with entries for journal
% articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
% book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
% and a homepage~\cite{ref_url1}. Multiple citations are grouped
% \cite{ref_article1,ref_lncs1,ref_book1},
% \cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{splncs04}
\bibliography{main}
%
% \begin{thebibliography}{8}
% \bibitem{ref_article1}
% Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)
% 
% \bibitem{ref_lncs1}
% Author, F., Author, S.: Title of a proceedings paper. In: Editor,
% F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
% Springer, Heidelberg (2016). \doi{10.10007/1234567890}
% 
% \bibitem{ref_book1}
% Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
% Location (1999)
% 
% \bibitem{ref_proc1}
% Author, A.-B.: Contribution title. In: 9th International Proceedings
% on Proceedings, pp. 1--2. Publisher, Location (2010)
% 
% \bibitem{ref_url1}
% LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
% Oct 2017
% \end{thebibliography}

>>>>

% Free variables
As usual, the variable $x$ is bound in $\lambda x:\tau.M$
and the transition variable $\alpha$ is bound in $\Lambda \alpha.M$.
We identify $\alpha$-convertible terms and assume the names of bound variables are pairwise distinct.
We write $\FV(M)$ and $\FTV(M)$ for the set of free variables and the set of free stage variables in $M$, respectively.

% Contexts
Contexts are sequences of triples of a variable, its type, and its stage.
$\textrm{Domain}$ is a function from a content to a set of variables defined in the context.
The side condition of $x\not\in\textrm{Domain}(\G)$ prevent multiple appearances of the same variable and
$x\not\in\textrm{FV}(\tau)$ is needed in the proof of Substitution Lemmas.

@@

\begin{align*}
	% \newcommand{\SB}{}
	(\lambda x:\tau.M)[\alpha \mapsto \epsilon] & = \lambda x:\tau[\alpha \mapsto \epsilon].M[\alpha \mapsto \epsilon]                                  \\
	(M\ N)[\alpha \mapsto \epsilon]             & = (M[\alpha \mapsto \epsilon])\ (N[\alpha \mapsto \epsilon])                                          \\
	(M\ \epsilon)[\alpha \mapsto \epsilon]      & = M[\alpha \mapsto \epsilon]\ \epsilon                                                                \\
	(\TB_\beta M)[\alpha \mapsto \epsilon]    & = \TB_\beta M[\alpha \mapsto \epsilon]                            & (\text{if } \alpha \neq \beta) \\
	(\TB_\beta M)[\alpha \mapsto \epsilon]    & = M[\alpha \mapsto \epsilon] & (\text{if } \alpha = \beta) \\
	(\TBL_\beta M)[\alpha \mapsto \epsilon]     & = \TBL_\beta M[\alpha \mapsto \epsilon]   & (\text{if } \alpha \neq \beta)                                 \\
	(\TBL_\beta M)[\alpha \mapsto \epsilon]     & =  M[\alpha \mapsto \epsilon]   & (\text{if } \alpha = \beta)                                 \\
	(\Lambda\beta.M)[\alpha \mapsto \epsilon] & = \Lambda\beta.M[\alpha \mapsto \epsilon]                         & (\text{if } \alpha \neq \beta) \\
	(\Lambda\beta.M)[\alpha \mapsto \epsilon] & = \Lambda\beta.M                                                  & (\text{if } \alpha = \beta)    \\
	(\%_\beta M)[\alpha \mapsto \epsilon]       & = \%_{\beta[\alpha \mapsto \epsilon]}M[\alpha \mapsto \epsilon] & (\text{if } \alpha \neq \beta) \\
	(\%_\beta M)[\alpha \mapsto \epsilon]       & = M[\alpha \mapsto \epsilon] & (\text{if } \alpha = \beta) \\
\end{align*}

@@

									% \section{First Section}
									% \subsection{A Subsection Sample}
									% Please note that the first paragraph of a section or subsection is
									% not indented. The first paragraph that follows a table, figure,
									% equation etc. does not need an indent, either.
									% 
									% Subsequent paragraphs, however, are indented.
									% 
									% \subsubsection{Sample Heading (Third Level)} Only two levels of
									% headings should be numbered. Lower level headings remain unnumbered;
									% they are formatted as run-in headings.
									% 
									% \paragraph{Sample Heading (Fourth Level)}
									% The contribution should contain no more than four levels of
									% headings. Table~\ref{tab1} gives a summary of all heading levels.
									% 
									% \begin{table}
									% \caption{Table captions should be placed above the
									% tables.}\label{tab1}
									% \begin{tabular}{|l|l|l|}
									% \hline
									% Heading level &  Example & Font size and style\\
									% \hline
									% Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
									% 1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
									% 2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
									% 3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
									% 4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
									% \hline
									% \end{tabular}
									% \end{table}
									% 
									% 
									% \noindent Displayed equations are centered and set on a separate
									% line.
									% \begin{equation}
									% x + y = z
									% \end{equation}
									% Please try to avoid rasterized images for line-art diagrams and
									% schemas. Whenever possible, use vector graphics instead (see
									% Fig.~\ref{fig1}).
									% 
									% \begin{figure}
									% \includegraphics[width=\textwidth]{fig1.eps}
									% \caption{A figure caption is always placed below the illustration.
									% Please note that short captions are centered, while long ones are
									% justified by the macro package automatically.} \label{fig1}
									% \end{figure}
									% 
									% \begin{theorem}
									% This is a sample theorem. The run-in heading is set in bold, while
									% the following text appears in italics. Definitions, lemmas,
									% propositions, and corollaries are styled the same way.
									% \end{theorem}
									% %
									% % the environments 'definition', 'lemma', 'proposition', 'corollary',
									% % 'remark', and 'example' are defined in the LLNCS documentclass as well.
									% %
									% \begin{proof}
									% Proofs, examples, and remarks have the initial word in italics,
									% while the following text appears in normal font.
									% \end{proof}
									% For citations of references, we prefer the use of square brackets
									% and consecutive numbers. Citations using labels or the author/year
									% convention are also acceptable. The following bibliography provides
									% a sample reference list with entries for journal
									% articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
									% book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
									% and a homepage~\cite{ref_url1}. Multiple citations are grouped
									% \cite{ref_article1,ref_lncs1,ref_book1},
									% \cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
									%
									% ---- Bibliography ----
									%
									% BibTeX users should specify bibliography style 'splncs04'.
									% References will then be sorted and formatted in the correct style.
									%
									\bibliographystyle{splncs04}
									\bibliography{main}
									%
									% \begin{thebibliography}{8}
									% \bibitem{ref_article1}
									% Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)
									% 
									% \bibitem{ref_lncs1}
									% Author, F., Author, S.: Title of a proceedings paper. In: Editor,
									% F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
									% Springer, Heidelberg (2016). \doi{10.10007/1234567890}
									% 
									% \bibitem{ref_book1}
									% Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
									% Location (1999)
									% 
									% \bibitem{ref_proc1}
									% Author, A.-B.: Contribution title. In: 9th International Proceedings
									% on Proceedings, pp. 1--2. Publisher, Location (2010)
									% 
									% \bibitem{ref_url1}
									% LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
									% Oct 2017
									% \end{thebibliography}
